Computing with an Angry Poker Player

### 2014-09-25 draft0.tex
added editing and writing tags
changed format of draft0

\documentclass[11pt]{article}
\usepackage{graphicx}    % needed for including graphics e.g. EPS, PS
\topmargin -1.5cm        % read Lamport p.163
\oddsidemargin -0.04cm   % read Lamport p.163
\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm 
%\pagestyle{empty}       % Uncomment if don't want page numbers
\parskip 7.2pt           % sets spacing between paragraphs
%\renewcommand{\baselinestretch}{1.5} % Uncomment for 1.5 spacing between lines
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{verbatim}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\parindent 0pt		 % sets leading space for paragraphs
\author{Perry Kleinhenz, Fermi Ma, and Erik Waingarten}
\title{18.821 - Poker Chips Finite board configurations}

\begin{document}         
\maketitle

In this file, we analyze the case where the initial number of chips is finite.
That is, the sum of all the chips on the board is finite.

\section{Standard Board}

@@

\section{Order of Redistribution}
\begin{definition}
We define a valid earthquake to be a small earthquake that occurs on a square that, at the time of the earthquake, has at least 4 chips.

@@

>>>>

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[margin=0.9in]{geometry}
%\usepackage{amsfonts}
%\usepackage{amsthm}
\usepackage{subfigure}
%\usepackage{caption}
%\usepackage{subcaption}
%\usepackage{cite}
\usepackage{hyperref}
\usepackage{url}
\urlstyle{same}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\makeatletter
\let\c@lemma=\c@theorem
\let\c@corollary=\c@theorem
\let\c@fact=\c@theorem
\makeatother

\let\realendproof=\endproof
\def\endproof{\hspace*{\fill}$\Box$\realendproof}

\begin{document}

\title{Computing with an Angry Poker Player}
\titlerunning{Computing with an Angry Poker Player}

\author{Perry Kleinhenz \and Fermi Ma \and Erik Waingarten}
%
\authorrunning{Perry Kleinhenz \and Fermi Ma \and Erik Waingarten}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{
\protect\url{{pkleinhe, fermima,eaw}@mit.edu}}

\maketitle

\section{Introduction}

Written by Fermi Ma, edited by Erik Waingarten and Perry Kleinhenz.

In this paper, we investigate the following problem set up:

\vbox{
\noindent
\begin{quote}
Each square of an infinite chess board contains some nonnegative number of poker chips. An earthquake hits one square that has at least four chips and redistributes them so that one chip moves in each of the four cardinal directions. 
\end{quote}
}
We also consider extensions of this problem set up where the earthquake hits all squares on the board at once. We refer to the former type of earthquake as $\textbf{local earthquakes}$ and earthquakes that hit the entire board as $\textbf{global earthquakes}$.
\section{Standard Board}

Written by Erik Waingarten, edited by Fermi Ma and Perry Kleinhenz

@@

\section{Order of Redistribution}

written by Fermi Ma and Perry Kleinhenz, edited by Erik Waingarten.

\begin{definition}
We define a valid earthquake to be a small earthquake that occurs on a square that, at the time of the earthquake, has at least 4 chips.

@@

written by Erik Waingarten, edited by Fermi Ma and Perry Kleinhenz
